Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-03-31 writeup/gz_hubble_data.tex
Paragraphs on metadata source

\title[Galaxy Zoo Hubble Data]{Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging}
\author[Lead Author \etal]{Lead Author and other Galaxy Zoo science team members\\
%
% List of people who have contributed (not sure if everyone will be author)
% Definitely: Lintott, Bamford, Edmondson, Masters, Simmons, Melvin, Willett, Galloway, Fortson, Schawinski, Cheung
% Others on GZ science team: Urry, Cardamone, Nichol, Kaviraj, Keel, Skibba, Thomas, Scarlata, Beck, Smethurst
% Tech: Smith, Parrish, Simpson, other devs?
% External: Han, Griffith
%
%$^1$Institute for Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth, PO1 3FX, UK \\
%$^2$South East Physics Network, www.sepnet.ac.uk\\
%$^3$Dept. of Astronomy, Cornell University, Space Sciences Building, Ithaca, NY 14850, USA\\
%$^2$Institute for Sciences of the Cosmos (ICCUB), University of Barcelona, Marti i Franques 1, Barcelona, 08024 Spain\\
%$^4$Oxford Astrophysics, Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
%$^5$Yale Center for Astronomy and Astrophysics, Yale University, P.O. Box 208121, New Haven, CT 06520, USA \\
%$^6$Steward Observatory, University of Arizona, 933 N. Cherry Ave, Tuscon, AZ 85721, USA\\
%$^4$Astronomy Department, Adler Planetarium and Astronomy Museum, 1300 Lake Shore Drive, Chicago, IL 60605, USA\\
%$^7$Centre for Astronomy \& Particle Theory, University of Nottingham, University Park, Nottingham, NG7 2RD, UK\\
%$^6$School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA\\
%$^7$Department of Physics \& Astronomy, 206 Gallalee Hall, 514 University Blvd., University of Alabama, Tuscaloosa, AL 35487-0234, USA\\
%$^8$Einstein Fellow\\ 
\\
 $^*$This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project. \\ Their contributions are individually acknowledged at \texttt{http://authors.galaxyzoo.org/authors.html}. \\
\\
{\tt E-mail: lead.author@university.edu}
 }

@@

For images from the ACS-GC \citet{gri12}, galaxies are identified using a combination of SExtractor \citep{ber96} and the galaxy-profile fitting framework \textsc{Galapagos} \citep{hau07}. We select all galaxies with $m < 23.5$, where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS + GOODS-S, and GOODS-N surveys, respectively.

Single-epoch images from SDSS Stripe~82 were selected using the same criteria from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ > 3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the $r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$. Coadded images from Stripe~82 were selected from the union of galaxies with coadded magnitudes brighter than $17.77$~mag and the galaxies detected in the single-depth images and matched to a coadd source. Of the images in the coadded sample, 5144/30339 (17 percent) are dimmer than this initial magnitude cut.

@@

\subsection{Artifically-redshifted images}

FERENGI images (ask Edmond to write this?) Should contain much of the information in \S\ref{sec:debiasing} right now.

\subsection{Redshifts}

We compiled redshifts from a variety of sources to include in the GZH catalog. For each galaxy, the redshift selected is in the $\tt Z\_Best$ column of the data (see Table~\ref{tbl:catalog_hst}), its type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog ($\tt ACSGC$ \citep{gri12}, $\tt 3DHST$ \citep{mom15}, $\tt MUSYC$ \citep{car10}, or $\tt UltraVISTA$ \citep{ilb13}) of the redshift is in column $\tt Z\_BEST\_SOURCE$.

@@

@@

In Figure~\ref{fig:p_vs_p} we examine the change in \pfeatures{} for the \ferengi{} galaxies relative to their lowest simulated redshift. In this analysis, only galaxies whose lowest simulated redshift image was ($\rm z_{sim}=0.3$) were used (see Table \ref{tbl:ferengivalues}), and only those which had detectable surface brightness measurements in \sextractor{}; this includes 3,950 of the total 6,466 images. For each simulated redshift value $z$, and at a fixed surface brightness $\mu$, we plot \pfeaturesz, the value measured at that simulated redshift, vs \pfeaturesrest, the value measured for the same galaxy imaged at $z=0.3$.

>>>>

\title[Galaxy Zoo Hubble Data]{Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging}
\author[Lead Author \etal]{Lead Author and other Galaxy Zoo science team members\\
%
% List of people who have contributed (not sure if everyone will be author)
% Definitely: Lintott, Bamford, Edmondson, Masters, Simmons, Melvin, Willett, Galloway, Fortson, Schawinski, Cheung
% Others on GZ science team: Urry, Cardamone, Nichol, Kaviraj, Keel, Skibba, Thomas, Wong, Scarlata, Beck, Smethurst
% Tech: Smith, Parrish, Simpson, other devs?
% External: Han, Griffith
%
%$^1$Institute for Cosmology and Gravitation, University of Portsmouth, Dennis Sciama Building, Burnaby Road, Portsmouth, PO1 3FX, UK \\
%$^2$South East Physics Network, www.sepnet.ac.uk\\
%$^3$Dept. of Astronomy, Cornell University, Space Sciences Building, Ithaca, NY 14850, USA\\
%$^2$Institute for Sciences of the Cosmos (ICCUB), University of Barcelona, Marti i Franques 1, Barcelona, 08024 Spain\\
%$^4$Oxford Astrophysics, Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
%$^5$Yale Center for Astronomy and Astrophysics, Yale University, P.O. Box 208121, New Haven, CT 06520, USA \\
%$^6$Steward Observatory, University of Arizona, 933 N. Cherry Ave, Tuscon, AZ 85721, USA\\
%$^4$Astronomy Department, Adler Planetarium and Astronomy Museum, 1300 Lake Shore Drive, Chicago, IL 60605, USA\\
%$^7$Centre for Astronomy \& Particle Theory, University of Nottingham, University Park, Nottingham, NG7 2RD, UK\\
%$^6$School of Physics and Astronomy, University of Minnesota, Minneapolis, MN 55455, USA\\
%$^7$Department of Physics \& Astronomy, 206 Gallalee Hall, 514 University Blvd., University of Alabama, Tuscaloosa, AL 35487-0234, USA\\
%$^8$Einstein Fellow\\ 
\\
 $^*$This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project. \\ Their contributions are individually acknowledged at \texttt{http://authors.galaxyzoo.org/authors.html}. \\
\\
{\tt E-mail: lead.author@university.edu}
 }

@@

For images from the ACS-GC \citet{gri12}, galaxies are identified using a combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting framework \textsc{Galapagos} \citep{hau07}. We selected all galaxies with $m < 23.5$, where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS + GOODS-S, and GOODS-N surveys, respectively. This yielded a total of 113,166~images (Table~\ref{tbl:gzh_numbers}).

Single-epoch images from SDSS Stripe~82 were selected using the same criteria from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ > 3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the $r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$. 21,522 galaxies in SDSS met these criteria. Coadded images from Stripe~82 were selected from the union of galaxies with coadded magnitudes brighter than $17.77$~mag and the galaxies detected in the single-depth images and matched to a coadd source. This resulted in a larger set of 30,339 images. Of the images in the coadded sample, 5144 (17~percent) are dimmer than the initial magnitude cut of 17.77.

@@

\subsection{Galaxy metadata}

Photometric data for the bulk of the GZH sample is largely drawn from the tables provided in \citet{gri12}. This includes photometric parameters from both \sextractor{} and \galfit, such as the fluxes, magnitudes, radii, ellipticities, position angles, and positions. \galfit{} also provides the parametric S\'{e}rsic index and effective half-light radius for the best-fit model. All parameters are measured in both bands of the ACS imaging, with the exception of the single-band COSMOS images.

Redshifts for the GZH catalog are compiled from a variety of sources to include in the GZH catalog. For each galaxy, the redshift selected is in the $\tt Z\_Best$ column of the data (see Table~\ref{tbl:catalog_hst}), its type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog ($\tt ACSGC$ \citep{gri12}, $\tt 3DHST$ \citep{mom15}, $\tt MUSYC$ \citep{car10}, or $\tt UltraVISTA$ \citep{ilb13}) of the redshift is in column $\tt Z\_BEST\_SOURCE$.

@@

Photometric and spectroscopic data for the SDSS Stripe~82 galaxies are taken from the CasJobs DR7 tables. This includes $ugriz$ Petrosian magnitudes and fluxes, as well as the relative de~Vaucouleurs and exponential fits from the model magnitudes. Redshifts used for the Sloan galaxies are all spectroscopic. 82.6\% of galaxies in the single-depth images and 65.1\% of galaxies in the coadd images have a measured DR7 spectroscopic redshift.

@@

In Figure~\ref{fig:p_vs_p} we examine the change in \pfeatures{} for the \ferengi{} galaxies relative to their lowest simulated redshift. In this analysis, only galaxies whose lowest simulated redshift image was ($\rm z_{sim}=0.3$) were used (see Table \ref{tbl:ferengivalues}), and only those which had detectable surface brightness measurements in \sextractor; this includes 3,950 of the total 6,466 images. For each simulated redshift value $z$, and at a fixed surface brightness $\mu$, we plot \pfeaturesz, the value measured at that simulated redshift, vs \pfeaturesrest, the value measured for the same galaxy imaged at $z=0.3$.
